Making multiple-locus association mapping on a genome-wide scale routine

### 2017-10-06 AM+draft.tex
061017 Just some minor tweaks to methods section - end of day

Suppose phenotypic and genotypic data are collected from a genome-wide association study involving $n$ individuals. 
Let $Y^{(n \times 1)}$ be a vector containing the quantitative trait data. Also, let $M^{(n \times L)}$ be a matrix of snp genotypes which have been collected from the $n$ individuals across $L$ snp loci. $M$ contains values -1, 0, and 1 corresponding to snp genotypes AA, AB, and BB, respectively.

To identify genomic regions which contain genes that influence the trait

We map genomic regions containing genes that influence the trait

>>>>

Suppose a genome-wide association study is conducted. Phenotypic and genotype data are collected.

Suppose phenotypic and genotypic data are collected from a genome-wide association study involving $n$ individuals. 
Let $y^{(n \times 1)}$ be a vector containing the quantitative trait data. 
Also, let $M^{(n \times L)} = [m_1 m_2 \ldots m_L]$ be a matrix of snp genotypes which have been collected from $L$ snp loci 
where $m_j^{(n \times 1)}$ is the vector of snp genotypes collected on the $j$ snp. 
The vector $m_j$  contains values -1, 0, and 1 corresponding to snp genotypes AA, AB, and BB, respectively.
